Viscous Erosion in Porous Media

### 2018-03-29 docs/methods/erosion_methods.tex
NM

As a final validation, we now aim to verify that our method converges with second-order accuracy in time. To this end, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 10^{-2}$. This stopping time is 56\% of the time it takes the body to vanish, and was selected so that the body will have eroded substantially but is not so small that accuracy is compromised. We assess error by measuring the difference between simulations of successive resolutions (i.e.~we verify Cauchy convergence). In particular, we measure the $L^2$-difference of the body shapes obtained at the stopping time. At each stage we halve the timestep $\Delta t$. Table \ref{convtab} shows the $L^2$-errors between successive simulations, along with the order of accuracy as obtained by Richardson-extrapolation-type calculations. The table confirms that our method to converges with second-order accuracy. In the table, we also show the CPU time of the simulation run on a single processor (though the algorithm is easily parallelized), showing a linear increase in computational time.

>>>>

As a final validation, we now verify that our method converges with the expected second-order accuracy in time. For this, we run the same single-body simulation from Figs.~\ref{01bodseq} and \ref{shrink_intface} (except with a coarser $N_\iin=256$) to a stopping time of $t_s = 10^{-2}$. This stopping time is 56\% of the vanishing time, and was selected so that the body will have eroded substantially but is not small enough to compromise accuracy (due to the stress diverging).
We assess error by measuring the $L^2$-difference in the body shape obtained from simulations of successive resolution, with $\Delta t$ halved at each stage. In Table \ref{convtab}, we report these errors along with the order of accuracy as obtained by Richardson-extrapolation-type calculations. The table confirms that our method converges with expected second-order accuracy. The last column of the table shows the CPU time taken for the simulation to run on a single-processor machine, demonstrating a nearly linear increase in computational time. Though the main parts of the algorithm are easily paralyzed, the single-processor times provide a simple assessment of method's complexity.
